The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-04-05 paper.tex
s/common mode noise pickup/common mode noise
After discussion with Harish we decideded this was a better term because
"pickup" is usually referred to RFI-like things.

The interferometer's sensitivity to $l=0$, however, deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
common-mode noise pick-up. In fact, the sensitivity of the interferometer is proportional to the
amplitude of these effects. For consistency we will include $a_{00}$ while solving
Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
because we do not have a measurement of cross-talk or common-mode noise pick-up.

>>>>

The interferometer's sensitivity to $l=0$, however, deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
common-mode noise. In fact, the sensitivity of the interferometer is proportional to the amplitude
of these effects. For consistency we will include $a_{00}$ while solving
Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
because we do not have a measurement of cross-talk or common-mode noise.
